---
title: "Performance Measures"
date: today
fig-width: 10
fig-asp: 0.3
format: 
    dashboard: 
        embed-resources: true
        theme: flatly
        scrolling: false
        expandable: false
        nav-buttons:
         - mastodon 
         - icon: github
           href: https://gitlab.com/
---

```{r}
library(dplyr)
library(RPamisc)
library(ggblanket)
library(glue)
library(gt)
library(purrr)
library(ggplot2)
library(reactable)
library(patchwork)
library(palmerpenguins)

set_blanket()

demo_data_raw <- 
    penguins |>
    filter(!is.na(flipper_length_mm)) |>
    mutate(
        short_bill_flag = if_else(bill_length_mm < 45, 1, 0),
        long_bill_flag = if_else(bill_length_mm >= 45, 1, 0),
        short_flipper_flag = if_else(flipper_length_mm <= 209, 1, 0),
        long_flipper_flag = if_else(flipper_length_mm > 209, 1, 0)
        )

demo_data_summary <- 
    demo_data_raw |>
    summarise(
        #.by = c(species),
        n = n(), 
        short_bill = sum(short_bill_flag, na.rm = TRUE),
        long_bill = sum(long_bill_flag, na.rm = TRUE),
        short_flipper = sum(short_flipper_flag, na.rm = TRUE),
        long_flipper = sum(long_flipper_flag, na.rm = TRUE)
    ) |>
    mutate(
        bill_rate = round(short_bill/n, 2),
        flipper_rate = round(short_flipper/n, 2)
        #rate = round(long_flipper/n, 2)
    ) 
     
demo_aggregate <- function(.data) {
    
results <- 
    .data |>
    summarise(
        #.by = c(species),
        n = n(), 
        short_bill = sum(short_bill_flag, na.rm = TRUE),
        long_bill = sum(long_bill_flag, na.rm = TRUE),
        short_flipper = sum(short_flipper_flag, na.rm = TRUE),
        long_flipper = sum(long_flipper_flag, na.rm = TRUE)
    ) %>%
    mutate(
        bill_rate = round(short_bill/n, 2),
        flipper_rate = round(short_flipper/n, 2)
        #rate = round(long_flipper/n, 2)
    ) %>%
    arrange(desc(bill_rate), n)

results

}
```


```{r}
set.seed(911)

month <- seq(as.Date("2024-01-01"), as.Date("2024-07-01"), "month")

demo_sample <- function(.data, month, size = 15) {

#    https://stackoverflow.com/questions/50977337/calling-prop-test-function-in-r-with-dplyr    
    .data |>
        slice_sample(n = size) |>
        demo_aggregate() |>
        mutate(month = month, .before = 1) |>
        mutate(rate = map2(short_flipper, n, ~ prop.test(.x, .y, conf.level=0.95) %>%
                                     broom::tidy())) %>%
        tidyr::unnest(rate) %>% 
        select(
            month, 
            n, 
            short_flipper, 
            everything()
        )
    
}

```

```{r}
# method 1
# sample of 15/month
method_1_data <-
    month |>
    map(~ demo_sample(demo_data_raw, .x, size = 15)) |>
    bind_rows()

set_blanket()

trend_plot <- function(.data, subtitle = "Method 1: sample 15") {
    
    .data |> 
       gg_pointrange(
            #subtitle = subtitle,
            x = month,  
            y = estimate,
            ymin = conf.low,
            ymax = conf.high,
            x_label = "",
            y_label = "",
            #y_label = "% Short Flipper", 
            y_labels = scales::percent,
            x_breaks = c(as.Date("2024-01-01"), as.Date("2024-07-01")),
            y_breaks = c(.2, .4, .6, .8, 1),
            y_expand_limits = c(.40, 1),
            #linewidth = 1, 
            ) +
        geom_line() +
        geom_hline(yintercept = .9, linetype = 'dashed') 
    
}

```


# Huddle Board 


## Sidebar {.sidebar}


_Refresh Date_: `r Sys.Date()`


- 30day Standardized Mortality Ratio - (SMR30)  
: Risk-adjusted Mortalities within 30 days of Acute Care admission, reported as an O/E ratio. Pre-admission Hospice cases are excluded.
- Cardiovascular Risk Management (CVRM)
: Composite score based on these components: A, B, C
- Comprehensive Risk Evaluation (CSRE)
: Percent of Positive CSSRS that had a timely CSRE (same day in ambulatory, 24 hours in UC and acute care)

## Main body

### Row 1 

```{r}
#| content: valuebox
#| title: "SMR30 O/E"
#| fig-cap: "caption"

  value = "1.5"
list(
  #icon = "graph-down-arrow",
  color = "light",
  value = value
)


```

```{r}
#| content: valuebox
#| title: "CVRM Composite"
  
value = "65%"

list(
  #icon = "graph-up-arrow",
  color = "danger",
  value = value 
)
```

```{r}
#| content: valuebox
#| title: "Days since last missed CSRE"
  
value = "5" 

list(
  #icon = "check2-square",
  color = "success",
  value = 5
)
```

### Row 2

#### Column 1 {width=20%}

::: {.card  title="Life Expectancy"}

That value box was created with R

:::


#### Column 2

```{r}
#| title: "CVRM"
#| fig-cap: "This is a caption"
 
demo_data_raw |>  
    gg_histogram(
        x = flipper_length_mm,
        #x = bill_length_mm,
        col = species,
        #facet2 = island, 
        facet = species
        )

```

### Row 3


#### Column 1 {width=20%}


::: {.card  title="Life Expectancy"}

__Hello world__  

That value box was created with R

:::

#### Column 2

```{r}
#| title: "CSRE"

p1 <- 
    method_1_data |>
    trend_plot()

p2 <- 
    method_1_data |>
    trend_plot()

p1 + p2

```


### Row 4 


#### Column 1 {width=20%}


::: {.card  title="Life Expectancy"}

## Hello world

That value box was created with R

:::

#### Column 2

```{r}
#| title: "CSRE"

p1 <- 
    method_1_data |>
    trend_plot()

p2 <- 
    method_1_data |>
    trend_plot()

p1 + p2

```

# Page 2

